---
title: "Meteorological Data Download"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: https://github.com/airqualityanthony/MetDataDashboard
    theme: simplex
---

```{r setup, include=FALSE}

library(flexdashboard)
library(openair)
library(leaflet)
library(viridis)
library(leaflet.extras)
library(httr)
library(jsonlite)
library(htmltools)
library(htmlwidgets)
library(dplyr)
library(visdat)
library(worldmet)
library(lubridate)


met_data_final <- readRDS("met_data_final.rds")
met_data_final$group[met_data_final$wd == 0] <- "grey"
met_data_final$group[between(met_data_final$wd,0.000000001,10)] <- "green"
met_data_final$date <- as.Date(met_data_final$date)

# store north arrow png
green_arrow <- "green_arrow.png"

orange_arrow <- "orange_arrow.png"

red_arrow <- "red_arrow.png"

grey_arrow <- "grey_arrow.png"

# make north arrow icon
grey_arrow.icon <- 
  makeIcon( iconUrl = grey_arrow
            , iconWidth = 20
            , iconHeight = 20 )
green_arrow.icon <-
  makeIcon( iconUrl = green_arrow
            , iconWidth = 20
            , iconHeight = 20 )

orange_arrow.icon <-
  makeIcon( iconUrl = orange_arrow
            , iconWidth = 20
            , iconHeight = 20 )
red_arrow.icon <-
  makeIcon( iconUrl = red_arrow
            , iconWidth = 20
            , iconHeight = 20 )

arrowIcons <- iconList(grey = grey_arrow.icon, green = green_arrow.icon,orange = orange_arrow.icon, red = red_arrow.icon)


rotatedMarker <- 
  htmlDependency( name = "Leaflet.rotatedMarker" # note: this .js file has to be copied and stored in your current working directory 
                  , version = "0.1.2"
                  , src = normalizePath( path = getwd() )
                  , script = "Leaflet.rotateMarker.js" )

registerPlugin <- function(map, plugin) {
  map$dependencies <- c(map$dependencies, list(plugin))
  map
}


date<-seq(as.Date("2019-01-01"), as.Date("2019-12-01"), by="day")
df = met_data_final

tilesURL <- "http://server.arcgisonline.com/ArcGIS/rest/services/Canvas/World_Light_Gray_Base/MapServer/tile/{z}/{y}/{x}"
points <- reactive({
    df %>% 
      filter(date==input$date)})
data <- reactiveValues(clickedMarker=NULL)


```
Meteorological Data
=====================================

Sidebar {.sidebar}
-----------------------------------------------------------------------

```{r}
# Define inputs
sliderInput("date","Animation Date",min(date),max(date),value = min(date),animate=T)

# Set up data download
data_for_dl <- reactive({
  
  download_data <- importNOAA(code = click_marker(), year = 2019)
  return(download_data)
})

output$downloadCSV <- downloadHandler(
  filename = 'data.csv',
  content = function(file) {
    write.csv(data_for_dl(), file)
  }
)



```
Click play to see the Met data animate over time. 

Click on a specific site in the map to see the data availability, THEN click on the download link below to return it's data for 2019. 

```{r}
downloadLink('downloadCSV', label = 'Download CSV for active site (2019)')
```

```{r}
output$downloadMET <- downloadHandler(
  filename = 'data.met', 
  content = function(file){
  cat("**************************************
  
  Data source: NOAA Integrated Surface Database (ISD) - https://www.ncdc.noaa.gov/isd
  Data extracted using the 'worldmet' package by David Carslaw - https://github.com/davidcarslaw/worldmet
  
  **************************************
  
  VARIABLES:
  8
  YEAR
  DAY
  HOUR
  U
  PHI
  CL
  T0C
  RHUM
  
            
  DATA:",
      paste(year(data_for_dl()$date),yday(data_for_dl()$date),hour(data_for_dl()$date),round(data_for_dl()$ws,digits = 2),round(data_for_dl()$wd,digits=4),data_for_dl()$cl,data_for_dl()$air_temp,data_for_dl()$RH, sep = ","),
      file = file,sep = "\n")
  
  })


```
You can also download the data formatted for ADMS by clicking the link below (do not change file extension name, just save as you would like it to be named, it will automaticall .MET file append)

```{r}
downloadLink('downloadMET', label = 'Download MET for active site (2019)')
```

Row
-----------------------------------------------------------------------

### Map

```{r}
# Draw the map without selected tracts
output$map <- renderLeaflet({
  map <- leaflet() %>%
      addTiles() %>%
      setView(-2.37,55.111,zoom = 5) %>%
      registerPlugin( plugin = rotatedMarker ) %>%
      addMarkers(data = points(),lng = ~longitude
                  , lat = ~latitude
                  , label = ~station
                  , layerId = ~code
                  , icon = ~arrowIcons[group]
                  , options = markerOptions( rotationAngle = ~wd - 180 ))
      
    map
    
  })
leafletOutput('map')
```

### Data Availability

```{r}
click_marker <- eventReactive(input$map_marker_click, {

  x <- input$map_marker_click

  return(x$id)

})

data_for_chart <- reactive({

  return(df[df$code == click_marker(), ])

})

output$visdata <- renderPlot({

  vis <- vis_miss(data_for_chart(),
           sort_miss = TRUE)

  vis

})
plotOutput('visdata')
```



About
============================================================================

The application is built with the [Shiny](http://shiny.rstudio.com) framework for the [R programming language](https://www.r-project.org/). The application layout is produced with the [flexdashboard](http://rstudio.github.io/flexdashboard/index.html) package, and the charts and maps use [visdat](https://github.com/ropensci/visdat) and [Leaflet.js](http://leafletjs.com/), all accessed through their corresponding R packages.  

Meteorological data is retrieved from NOAA Integrated Surface Database using the [worldmet](http://davidcarslaw.github.io/worldmet/) R package. 

Code for the dashboard is linked in the top right and available at <https://github.com/airqualityanthony/MetDataDashboard>.  

I welcome feedback and suggestions on the github page.

To Do: 

- merge more met data into sites from other sources
- Selectable years

